|

### 2021-11-08 paper/dcpo_demsupport.Rmd
adding corrected data descriptions for #34; cleaning the setup chunk for #29

# load all the packages you will use below 
p_load(
  # analysis
  plm, 
  # presentation
  gridExtra,
  modelsummary,
  # drhutools, # for colorful plots
  dotwhisker, 
  latex2exp,
  # data wrangling
  here,
  broom,
  tidyverse, 
  glue
)

@@

source(here("R", "tidy_pgmm.r"))
source(here("R", "moc_function.R")) 
source(here("R", "moc_summary.R")) 
source(here("R", "customFunctions.R"))

# dotwhisker::small_multiple() hacks
body(small_multiple)[[19]] <- substitute(
  p <- ggplot(df, aes(y = estimate, ymin = conf.low, ymax = conf.high, 
                      x = as.factor(model), colour = submodel)) +
    do.call(geom_pointrange, point_args) + 
    ylab("") + xlab("") + 
    facet_grid(term ~ .,
               scales = "free",
               labeller = label_parsed,    # enable LaTeX facet labels
               switch = "y") +             # put facet labels on left
    scale_y_continuous(position = "right") # put axis label on right
)

theme_set(theme_bw())
```

```{r data-input, include=FALSE, cache=TRUE}
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/2hwqg/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/wfm3c/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/rvc92/download
load(here("data","claassen_replication_input.rda"))
load(here("data","exp_claassen_input.rda"))
#load(here("data","dcpo_apsr.rda"))
#load(here("data","dcpo_ajps.rda"))

@@

mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
mocdcpo_APSR <- readRDS(here("output","estimates_moc_dcpoAPSR.RDS"))
mocresult_dcpoAJPS <- readRDS(here("output","estimates_moc_dcpoAJPS.RDS"))
```

@@

Note that, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735." 
We follow the replication file in the following tables.

>>>>

# load all the packages you will use below
p_load(
    # analysis
    plm,

    # presentation
    gridExtra,
    modelsummary,
    drhutools, ## for colorful plots
    dotwhisker,
    latex2exp,

    # data wrangling
    here,
    broom,
    tidyverse,
    glue)

@@

source(here("R", "customFunctions.R")) ## analyzing and presenting functions

theme_set(theme_bw())

## dotwhisker::small_multiple() hacks
body(small_multiple)[[19]] <- substitute(
    p <-
        ggplot(
            df,
            aes(
                y = estimate,
                ymin = conf.low,
                ymax = conf.high,
                x = as.factor(model),
                colour = submodel
            )
        ) +
        do.call(geom_pointrange, point_args) +
        ylab("") + xlab("") +
        facet_grid(
            term ~ .,
            scales = "free",
            labeller = label_parsed,
            # enable LaTeX facet labels
            switch = "y"
        ) +             # put facet labels on left
        scale_y_continuous(position = "right") # put axis label on right
)

```{r data-input, include=FALSE, cache=TRUE}
## Replication data
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/2hwqg/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/wfm3c/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/rvc92/download
load(here("data", "exp_claassen_input.rda")) # Source???

## Preload chunk-produced results to speed up the compiling
## One can find how they were created by locating the corresponding chunks

@@

mocresult_correctAJPS <-
    readRDS(here("output", "estimates_moc_correctAJPS.RDS"))
mocresult_expAJPS <-
    readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
mocresult_correctAPSR <-
    readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
mocresult_expAPSR <-
    readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
mocdcpo_APSR <- readRDS(here("output", "estimates_moc_dcpoAPSR.RDS"))
mocresult_dcpoAJPS <-
    readRDS(here("output", "estimates_moc_dcpoAJPS.RDS"))
```

@@

During the replications of @Claassen2020a;@Claassen2020b, we found several miscoding across the original data.
For example, in @Claassen2020b that the author coded the option "Necesitamos un líder fuerte que no tenga que ser elegid" as "strong_lapop_2" for the question:

> Hay gente que dice que necesitamos un líder fuerte que no tenga que ser elegido a través del voto. AUT1 Otros dicen que aunque las cosas no funcionen, la democracia electoral, o sea el voto popular, es siempre
lo mejor. ¿Qué piensa usted? [Leer alternativas]

But according to the description of the question, this ought to be "strong_amb_1."
Another example involves a miscount of the midpoint of its three-point scale as a positive, democracy-supporting response, when the original work coded "evdemoc_asiab" in the Asian Barometer.
In a separate ongoing research project, we will identify the main types of miscoding and evaluate the extent to which they affect on the inferences.
In this work, we use the corrected data for the replications with uncertainty to ensure that the data quality would not distort the results.

Moreover, for the GMM models, the original publication presented the observation number based on the trimmed data, i.e., "2435", while the tabulating function in the replication file (line 86) uses the full used-observation number, "4735." 
We follow the replication file in the following tables.
